\documentclass[12pt,preprint]{aastex}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\vk}{von K\'{a}rm\'{a}n}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}
\slugcomment{Draft version}
 
\shorttitle{A Study of the Point Spread Function at SDSS}
\shortauthors{Xin, Ivezi\'{c} and Friends}
 
\begin{document}

\title{A Study of the Point Spread Function in SDSS Images}    %line break \\ is allowed in title

\author{B. Xin$^1$, \v{Z}. Ivezi\'{c}$^2$, R.H. Lupton$^3$, P. Yoachim$^2$, R.L. Jones$^2$, C. Claver$^1$, G. Angeli$^{1*}$}
\and
\author{Other Contributors}

\affil{$^1$Large Synoptic Survey Telescope, Tucson, AZ 85719}
\affil{$^2$Department of Astronomy, University of Washington, Seattle, WA 98195}
\affil{$^3$Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544}
\altaffiltext{*}{Current address: Giant Magellan Telescope
  Organization, Pasadena, CA 91107}

\begin{abstract}
We use SDSS imaging data in $ugriz$ passbands to study the shape of
point spread function (PSF) profile and the variation of its width with 
wavelength and time. We find that the PSF profile is well described by 
theoretical predictions based on \vk's turbulence theory. The observed 
profile can be parametrized by two parameters, the profile's FWHM (full width
at half maximum) and a normalization of the contribution of an empirical
instrumental PSF. The profile shape is very similar to the ``double gaussian
plus power-law wing'' decomposition used by SDSS, but here it is modeled 
with two free model parameters, rather than six as in SDSS pipeline. 
The FWHM variation with wavelength folows the
$\lambda^{\alpha}$ power law, where $\alpha \approx-0.3$, and is correlated
with the FWHM itself. This behavior is much better described by \vk's turbulence 
theory with the outer scale parameter in the range 10--30 m, than by the 
Kolmogorov's turbulence theory. We also measure the temporal and angular
structure functions for FWHM and compare them to simulations and
existing measurements.
The angular structure function saturates around 0.5$-$1.0 degree. 
The temporal behavior is found to be consistent with the damped random
walk model with a characteristic timescale of $\sim$ 15 minutes.
\end{abstract}

\keywords{imaging point spread function --- SDSS}
 


\section{Introduction}

\input{intro} 

\section{Data Overview} 

\input{data_overview} 


\section{The PSF profile analysis}

\input{PSFprofile} 

\section{The analysis of FWHM behavior} 

\input{FWHManalysis} 

\section{Discussion and Conclusions} 

\input{conclusions} 


\acknowledgments




%% To help institutions obtain information on the effectiveness of their
%% telescopes, the AAS Journals has created a group of keywords for telescope
%% facilities. A common set of keywords will make these types of searches
%% significantly easier and more accurate. In addition, they will also be
%% useful in linking papers together which utilize the same telescopes
%% within the framework of the National Virtual Observatory.
%% See the AASTeX Web site at http://aastex.aas.org/
%% for information on obtaining the facility keywords.

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided 
%% in parentheses, after the keyword, but they will not be verified.

{\it Facilities:} \facility{SDSS}, \facility{LSST}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

%\appendix
%
%\section{Appendix material}

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.


\bibliographystyle{aj}
\bibliography{sdsspsf}


%% The following command ends your manuscript. LaTeX will ignore any text
%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

----------Completed: ----------------

ZI:  find exact definition of neff_psf (is it based on fit or input data?) 
Bo: add analysis directory and py code 


1)  make files, one per run, as a function of field number, with
- field, camera column, bandpass, 
- one-parameter fit FWHM from fitting \vk profile
- other SDSS params: psf_width, airmass, mjd, psf_nstar, neff_psf, sky_frames 


E.g. for some run
#  field  camCol  filter   FWHMvK    (other SDSS params)

2) plot FWHMvK vs. psf_width for 30 panels 

-----use a Gaussian as convolution kernel, remake fits -------

Bo:
check neff_psf from the vK fit and compare to 2G fit.
(checked fwhmeff, i.e., fwhmvk, and compared to psf_width from the 2G
fit. Generally the agreement is good. When they don't agree very well,
visually checking the vK fit vs the 2G fit shows that the vK fit often
gives the more reasonable agreement between data and fit.)
------make RMS (x - data) plots to quantify -----------
            /n(-1?) for 1-4, 5+ separately
            exclude bad 2G fits

3) plot alpha (index for lambda dep.) histograms for all data and for 
    two realizations of ``longest stretch'' selection
(not very conclusive, due to z-band tipping upward. The i-band could
be problematic too)

----------to do ----------------

---alpha vs seeing, col#6, col#3
??? masterTXT, a column to flag failed 2D fits?
???(in the master txt file for alpha, add seeing as a column)

4) plot profiles for a range of fields when the seeing is rapidly changing (is profile shape changing?) 


-------------Analysis structure: -----------------

1) profile discussion
- compare to SDSS, emphasize 1 parameter vs. 6 parameters
- discuss profile shape stability when seeing is changing rapidly

2) dependence on wavelength

- what is alpha distribution? 

3) cross-correlation of camera columns and measurement of structure function
    (that is, the covariance vs. angular distance) 

---for each run, each filter, make plot of cov vs separation
----fit through (0,1), plot slope as a function of seeing

4) auto-correlation function (and power spectrum) for temporal variation

- let's start with plain Fourier transform and look at power spectra (we can 
    play games with co-addition, 6 columns for a given run, or all runs)
- potentially, we could also look at  Kelly and Becker code  (2014, ApJ 788, 33) 
- here we can compare to Chuck's CP measurements (in opsim db) 

---for each run, each filter, camcol (#2,3), make D vs frequency.


Adaptive Beaming and Imaging in the Turbulent Atmosphere 
by Vladimir P. Lukin; Boris V. Fortes, Chapter 3, SPIE Press Book.
Fig 3: the depdendence of FWHM on D, Lo and lambda 




FWHM vs. field analysis

1040: 122 fields, oscillations on 5 min timescale, look at PSD 
2583: 227 fields, excellent seeing (1.1 in r) 
2662: 469 fields, long with typical seeing, with worst at the end
2709: 263 fields, oscillations on 5 min timescale, look at PSD 
2728: 488 fields, long with good seeing (1.2 in r) 
3325: 493 fields, long with typical seeing, with worst at the start
3360: 513 fields, typical but very variable seeing
3384: 784 fields, a long and *very* oscillatory run
3388: 713 fields, very different PSD than for 3384 
4145: 505 fields, steady deterioration from 1 arcsec to ~2 arcsec
4198: 747 fields, another long run with typical and oscillatory seeing
4203: 777 fields, another long run
4207: 753 fields, another long run
4849: 918 fields, a long run, typical seeing 
4868: 609 fields, another long run
4874: 981 fields, the longest run, typical seeing   *poster child* 


I would exclude runs with fewer than 100 fields from our analysis 